Rotation and Lithium Confirmation of a 500 Parsec Halo for the Open Cluster NGC\,2516\footnote{This is paper 3 of the Cluster Difference Imaging Photometric Survey.}

### 2021-04-22 cluster_paper/maintable_header.tex
update with my own Li EW fitting
the magic M dwarf EW vs Teff relation has disappeared.

%% General table comment marker
\tablecomments{
Table~\ref{tab:maintable} is published in its entirety in a
machine-readable format.  One entry is shown for guidance regarding
form and content.  This table is a concatenation of all candidate
NGC\,2516 members reported by \citetalias{cantatgaudin_gaia_2018},
\citetalias{kounkel_untangling_2019}, and \citetalias{meingast_2021}
based on the Gaia DR2 data.  Different levels of purity and
completeness can be achieved using different cuts on
photometric periods and lithium eqiuvalent widths (see
Figure~\ref{fig:rot}).  Sets $\mathcal{A}$ and $\mathcal{B}$ provide
two levels of cleaning based on rotation periods that may be useful.
Note that when the target star is the only star present in the TESS
aperture, \texttt{nequal}$=0$, \texttt{nclose}$=1$, and
\texttt{nfaint}$=1$.
}
\vspace{-0.5cm}
\end{deluxetable*}

>>>>

%% General table comment marker
\tablecomments{
Table~\ref{tab:maintable} is published in its entirety in a
machine-readable format.  One entry is shown for guidance regarding
form and content.  This table is a concatenation of all candidate
NGC\,2516 members reported by \citetalias{cantatgaudin_gaia_2018},
\citetalias{kounkel_untangling_2019}, and \citetalias{meingast_2021}
based on the Gaia DR2 data.  Different levels of purity and
completeness can be achieved using different cuts on photometric
periods and lithium eqiuvalent widths (see Figure~\ref{fig:rot}).
Sets $\mathcal{A}$ and $\mathcal{B}$ provide two possible levels of
cleaning based on rotation periods.  Note that when the target star is
the only star present in the TESS aperture, \texttt{nequal}$=0$,
\texttt{nclose}$=1$, and \texttt{nfaint}$=1$.  The light curves are
available at \url{https://archive.stsci.edu/hlsp/cdips}.
}
\vspace{-0.5cm}
\end{deluxetable*}
